An Embedding Framework for Consistent Polyhedral Surrogates

### 2021-10-20 poly-embed-journal/poly-embed-journal.tex
one more note
Hopefully not creating a conflict

\begin{definition}[$\epsilon$-thickened link] \label{def:eps-thick-link}
  First, define $\U = \{\Gamma(p) : p \in \simplex\}$ and, for each $U \in \U$, let $R_U = \{r \in \R : \phi(r) \in U\}$, the reports whose embedding points are in $U$.
  Given a polyhedral $L$ that embeds some $\ell$, an $\epsilon > 0$, and a norm $\|\cdot\|$, the \emph{$\epsilon$-thickened link} $\psi$ is constructed as follows.
  First, initialize $\Psi: \reals^d \toto \R$ by setting $\Psi(u) = \R$ for all $u$.
  Then for each $U \in \U$, for all points $u$ such that $\inf_{u^* \in U} \|u^*-u\| < \epsilon$, update $\Psi(u) = \Psi(u) \cap R_U$.
  Finally, define $\psi(u) \in \Psi(u)$, breaking ties arbitrarily.
  If $\Psi(u)$ became empty, then leave $\psi(u)$ undefined.
\end{definition}
A key point is that, by Lemma~\ref{lem:polyhedral-range-gamma}, there are only finitely many sets of the form $U = \Gamma(p)$.
We then show, along the lines discussed above, that for a small enough choice of $\epsilon > 0$, if the thickenings of $U$ and $U'$ overlap at some $u$, then the corresponding report sets $R_U, R_{U'}$ also overlap; this implies $\Psi(u)$ is nonempty.
Given a well-defined thickened link $\psi$, calibration is almost immediate because, given $p$, any report $u$ linking to a suboptimal $r = \psi(u)$ satisfies $\inf_{u^* \in \Gamma(p)} \|u^* - u\| \geq \epsilon$.
  We then show that the minimal gradient of the expected loss along any direction away from $U$ is lower-bounded, giving a constant excess expected loss at $u$.

>>>>

\begin{definition}[$\epsilon$-thickened link] \label{def:eps-thick-link}
  First, define $\U = \{\Gamma(p) : p \in \simplex\}$ and, for each $U \in \U$, let $R_U = \{r \in \R : \varphi(r) \in U\}$, the reports whose embedding points are in $U$.
  Given a polyhedral $L$ that embeds some $\ell$, an $\epsilon > 0$, and a norm $\|\cdot\|$, the \emph{$\epsilon$-thickened link} $\psi$ is constructed as follows.
  First, initialize $\Psi: \reals^d \toto \R$ by setting $\Psi(u) = \R$ for all $u$.
  Then for each $U \in \U$, for all points $u$ such that $\inf_{u^* \in U} \|u^*-u\| < \epsilon$, update $\Psi(u) = \Psi(u) \cap R_U$.
  Finally, define $\psi(u) \in \Psi(u)$, breaking ties arbitrarily.
  If $\Psi(u)$ became empty, then leave $\psi(u)$ undefined.
\end{definition}
A key point is that, by Lemma~\ref{lem:polyhedral-range-gamma}, there are only finitely many sets of the form $U = \Gamma(p)$.
We then show, along the lines discussed above, that for a small enough choice of $\epsilon > 0$, if the thickenings of $U$ and $U'$ overlap at some $u$, then the corresponding report sets $R_U, R_{U'}$ also overlap; this implies $\Psi(u)$ is nonempty.
Given a well-defined thickened link $\psi$, calibration is almost immediate because, given $p$, any report $u$ linking to a suboptimal $r = \psi(u)$ satisfies $\inf_{u^* \in \Gamma(p)} \|u^* - u\| \geq \epsilon$.
  We then show that the minimal gradient of the expected loss along any direction away from $U$ is lower-bounded, giving a constant excess expected loss at $u$.
